Gastro-intestinal transmission of _Clostridioides difficile_ and antimicrobial-resistant bacteria in healthcare settings -- calibration of an agent-based model

### 2025-10-28 paper/paper.qmd
out_random path in paper

```{r load-pre-processed-data, include=FALSE}
# Alternatively, just load previously dumped .RData from a run of calibrate.R
load(file.path("..", "out", "calibrate.RData"))
```

>>>>

```{r load-pre-processed-data, include=FALSE}
# Alternatively, just load previously dumped .RData from a run of calibrate.R
load(file.path("..", "out_random", "calibrate.RData"))
```
